How to compute the fusion product of MV cycles in type A

### 2021-04-19 draft.tex
whatd i forget

    Since stable MV cycles can be represented by ordinary ones the multiplicities in 
    $$
    b_{Z'}b_{Z''} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} i \left(
        Z, Z' \circ Z''
        % \pi^{-1}(0) \cdot \overline{Z_1 \times Z_2 \times U}
    \right) b_Z 
    $$
    can also be deduced from \Cref{eq:tabmult} for appropriate choices of $\lambda',\lambda''$ and $\mu',\mu''$. These are described in \Cref{lem:mintab,prop:minwts} below.
\end{proposition}
% 
\begin{conjecture}
    % Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu_2$. 
    Let $\tau$ be the tableau of shape $\lambda$ and weight $\mu$ whose Lusztig datum is equal to the sum of the Lusztig data of $\tau'$ and $\tau''$. 
    % Then $i(\tau, \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U})$ is equal to 1. 
    Then 
    \begin{equation}
        i(\tau, 
        % \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U}
        % Z_1 \circ Z_2 
        \tau' \circ \tau''
        ) = 1 \,. 
    \end{equation}
\end{conjecture}
%

@@

% Dimensions: $(1,0,-1)$ for both.

@@

\begin{example}
Consider the product $Z_{in} * Z_{out}$, so the tableaux are 
\[
\young(2,4) \text{ and } \young(13,2,4).
\]
As the sum of the weights is not dominant, we will instead be using the tableaux
\[
\young(112,24,3) \text{ and } \young(13,2,4).
\]
Our matrix is 
\[
X = \left[\begin{BMAT}(e){ccc;ccc;cc;cc}{ccc;ccc;cc;cc}
    0 & 1 & & & & & & & & \\
     & 0 & 1 & & & & & & & \\
     & & s & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{13}^1 & A_{13}^2 & A_{14}^1 & A_{14}^2 \\
     & & & 0 & 1 & & & & & \\
     & & & & 0 & 1 & & & & \\
     & & & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 & A_{24}^2 \\
     & & & & & & 0 & 1 & & \\
     & & & & & & & s & A_{34}^1 & A_{34}^2 \\
     & & & & & & & & 0 & 1 \\
     & & & & & & & & & s
\end{BMAT}
\right]
\]
The relations from the submatrices are:
\[
\begin{array}{c|c}
    \text{Submatrix} & \text{Relations} \\ \hline
    X_2 & A_{12}^1, A_{12}^2+sA_{12}^3 \\
    X_3 & A_{13}^1,A_{23}^1 \\
    X_4 & \begin{array}{c}
         A_{23}^2A_{34}^1 - sA_{24}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
         A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\
         A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, \\
         A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
         A_{12}^3A_{13}^2A_{24}^1A_{34}^2 - A_{12}^2A_{13}^2A_{24}^2A_{34}^2 + A_{12}^3A_{14}^1A_{24}^1 - A_{12}^2A_{14}^2A_{24}^1
    \end{array} 
\end{array}.
\]
Hence our ideal decomposes into 
\[
\langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle
\cap \begin{array}{c}
     \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
     A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle. 
\end{array} 
\]
The tableau for each ideal is
\[\begin{array}{cccc}\vspace{1mm}
    \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle &\leadsto \young(11124,223,34) &\equiv \young(24,3,4) &\leadsto Z_{P_1} Z_{P_3} \\ 
    \begin{array}{c}
     \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
     A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle. 
\end{array} &\leadsto \young(11123,224,34) &\equiv \young(123,24,4) &\leadsto Z_1 Z_3 Z_{P_2}
\end{array}
\]
so $Z_{in} * Z_{out} = Z_{P_1} Z_{P_3} + Z_1 Z_3 Z_{P_2}$.
\end{example}

>>>>

    Since stable MV cycles can be represented by ordinary ones the multiplicities in 
    $$
    b_{Z'}b_{Z''} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} i \left(
        Z, Z' \circ Z''
        % \pi^{-1}(0) \cdot \overline{Z_1 \times Z_2 \times U}
    \right) b_Z 
    $$
    can also be deduced from \Cref{eq:tabmult} for appropriate choices of $\lambda',\lambda''$ and $\mu',\mu''$. These are described in \Cref{lem:mintab,prop:minwts} below.
\end{proposition}
% 
\begin{conjecture}
    % Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu  _2$. 
    Let $\tau$ be the tableau of shape $\lambda$ and weight $\mu$ whose Lusztig datum is equal to the sum of the Lusztig data of $\tau'$ and $\tau''$. 
    % Then $i(\tau, \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U})$ is equal to 1. 
    Then 
    \begin{equation}
        i(\tau, 
        % \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U}
        % Z_1 \circ Z_2 
        \tau' \circ \tau''
        ) = 1 \,. 
    \end{equation}
\end{conjecture}
%

@@

Dimensions: $(1,0,-1)$ for both.

@@

\begin{example}
Consider the product $Z_{in} * Z_{out}$, so the tableaux are 
\[
\young(2,4) \text{ and } \young(13,2,4).
\]
As the sum of the weights is not dominant, we will instead be using the tableaux
\[
\young(112,24,3) \text{ and } \young(13,2,4).
\]
Our matrix is 
\[
X = \left[\begin{BMAT}(e){ccc;ccc;cc;cc}{ccc;ccc;cc;cc}
    0 & 1 & & & & & & & & \\
     & 0 & 1 & & & & & & & \\
     & & s & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{13}^1 & A_{13}^2 & A_{14}^1 & A_{14}^2 \\
     & & & 0 & 1 & & & & & \\
     & & & & 0 & 1 & & & & \\
     & & & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 & A_{24}^2 \\
     & & & & & & 0 & 1 & & \\
     & & & & & & & s & A_{34}^1 & A_{34}^2 \\
     & & & & & & & & 0 & 1 \\
     & & & & & & & & & s
\end{BMAT}
\right]
\]
The relations from the submatrices are:
\[
\begin{array}{c|c}
    \text{Submatrix} & \text{Relations} \\ \hline
    X_2 & A_{12}^1, A_{12}^2+sA_{12}^3 \\
    X_3 & A_{13}^1,A_{23}^1 \\
    X_4 & \begin{array}{c}
         A_{23}^2A_{34}^1 - sA_{24}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
         A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\
         A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
         A_{12}^3A_{13}^2A_{24}^1A_{34}^2 - A_{12}^2A_{13}^2A_{24}^2A_{34}^2 + A_{12}^3A_{14}^1A_{24}^1 - A_{12}^2A_{14}^2A_{24}^1
    \end{array} 
\end{array}.
\]
Our ideal decomposes into 
\[
\langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle
\cap \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle.
\]
The tableau for each ideal is
\[\begin{array}{cccc}\vspace{1mm}
    \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle &\leadsto \young(11124,223,34) &\equiv \young(24,3,4) &\leadsto Z_{P_1} Z_{P_3} \\ 
    \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle &\leadsto \young(11123,224,34) &\equiv \young(123,24,4) &\leadsto Z_1 Z_3 Z_{P_2}
\end{array}
\]
so $Z_{in} * Z_{out} = Z_{P_1} Z_{P_3} + Z_1 Z_3 Z_{P_2}$.
\end{example}
